What do incoming university students believe about open science practices in

### 2021-10-29 analysis/Manuscript.Rmd
update minor changes

keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
- id: '3'
  institution: Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology
editor_options: 
  chunk_output_type: console
csl               : "apa.csl" 
---

@@

```{r setup, include = FALSE}
library(papaja) #install with devtools1
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

<!--MW: The paragraphs above contain some numeric info that's written in manually rather than being R outputs (e.g., "three", "seven") 
Not sure if that's a worry. JB: It sort of has to be because a) it's a holistic summary
and b) APA requires numbers below 10 to written out.
-->

<!-- JB: More of a concern for me is that we don't say anything about the 
correlations. If we aren't going to say anything about them at all, we can 
include them as a supplemental material? We preregistered them, so we have to 
include them, but we don't really have to say anything about them.-->

>>>>

keywords: open science, psychology, teaching, reproducibility, replication
wordcount:
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
- id: '3'
  institution: Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology
editor_options: 
  chunk_output_type: console
csl               : "apa.csl" 
---

@@

```{r setup, include = FALSE}
library(papaja) #install with devtools1
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(psych) #for correlation matrices
library(tidyselect) 
#library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@
